Constraints on Cosmic-Ray Particle Populations, Magnetic Fields, and Dark Matter from VHE Gamma-Ray Observations of the Coma Cluster of Galaxies with VERITAS

### 2011-08-08 ms.tex
More DM edits
Fermi analysis for XCR and B limits added

\documentclass[12pt,manuscript]{aastex}
%%\documentclass[twocolumn]{emulateapj}

@@

\begin{deluxetable}{cccccccccccc}
\tablecolumns{12}
\tablewidth{0pc}
\tablecaption{Constraints on relative CR pressure in the Coma cluster core for different spatial extensions} \rotate
\tabletypesize{\small}
\tablehead{
\colhead{RoI\tablenotemark{a} [deg]} 
    & \colhead{$F_\rmn{sim}(E)$\tablenotemark{b}} & \colhead{$F_\rmn{sim}(>E)$\tablenotemark{c}} 
    & \multicolumn{3}{c}{analytic model: $X_{\CR,\,\rmn{max}}~[\%]$\tablenotemark{d} } 
    & \multicolumn{3}{c}{$F_{\gamma,\,\rmn{min}}(>E)$\tablenotemark{e}} 
    & \multicolumn{3}{c}{$X_{\CR,\,\rmn{min}}~[\%]$\tablenotemark{f} } \\
& & & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
    & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
    & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
}
\startdata
0 & -     & -    & 10   & 23 & 97 & 1.6 & 0.7 & 0.3 & 0.067 & 0.061 & 0.11 \\
0.2  & 0.80  & 2.9  & 4.8  & 10 & 43 & 3.1 & 1.4 & 0.6 & 0.078 & 0.072 & 0.13 \\
0.4  & 1.21  & 4.4  & 6.7  & 15 & 62 & 6.3 & 2.8 & 1.3 & 0.098 & 0.090 & 0.16
\enddata
\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the analysis PSF.}
\tablenotetext{b}{Differential gamma-ray flux $E^{2}dF/dE$ at $E=220$ GeV in units of $10^{-6}$ GeV m$^{-2}$ s$^{-1}$ in the simulation-based analytic model by \citet{article:PinzkePfrommer:2010}. }
\tablenotetext{c}{Integrated gamma-ray flux above $E=220~\rmn{GeV}$ in units of $10^{-9}$ ph. m$^{-2}$ s$^{-1}$; simulation-based analytical model by \citet{article:PinzkePfrommer:2010}.} 
\tablenotetext{d}{Constraint on the relative CR pressure, $X_{\CR} = \expval{P_\CR}/ \expval{P_\rmn{th}}$, which was assumed to be constant through the cluster and calculated according to \citet{article:PfrommerEnsslin:2004b}.}
\tablenotetext{e}{Minimum gamma-ray flux in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ of the hadronic model described in the text.}
\tablenotetext{f}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/F$, for energies $E>220~\rmn{GeV}$ in the hadronic model described in the text.}
\label{table:constraints}
\end{deluxetable}

\begin{deluxetable}{cccc}
\tablecolumns{4}
\tablewidth{0pc}
\tablecaption{Constraints on magnetic fields in the hadronic model of the radio halo of Coma cluster}
\tablehead{
\colhead{$\alpha_{B}$} &
\multicolumn{3}{c}{Minimum magnetic field, $B_0~[\mu\rmn{G}]$}\\
\colhead{} & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
}
\startdata
0.3 & 0.61 & 0.51 & 0.43 \\
0.5 & 0.82 & 0.68 & 0.58 \\
0.7 & 1.19 & 0.98 & 0.83 
\enddata
\tablecomments{The parameters of the magnetic field are the magnetic decline, $\alpha_B$, and the central field strength, $B_{0}$, which are defined by $B(r) = B_{0}\,[n_\rmn{e}(r)/n_{\rmn{e}}(0)]^{\alpha_B}$.}
\label{table:Bmin}
\end{deluxetable}

@@

\begin{deluxetable}{lccc}
\tablecolumns{4}
\tablewidth{0pc}
\tablecaption{Limits on the DM annihilation cross section $\expval{\sigma v}$.}
\tablehead{
\colhead{Channel} & RoI [deg] & $m_{\chi}$ [GeV] & $\expval{\sigma v}$ [cm$^{3}$ s$^{-1}$]
}
\startdata
W$^{+}$W$^{-}$ & 0 & 2000 & $1.1\times 10^{-20}$ \\
& 0.2 & 1900 & $4.3\times 10^{-21}$ \\
& 0.4 & 1900 & $8.4\times 10^{-21}$ \\
$b\bar{b}$ & 0 & 3500 & $1.2\times 10^{-20}$ \\
& 0.2 & 3400 & $4.4\times 10^{-21}$ \\
& 0.4 & 3500 & $8.7\times 10^{-21}$ \\
$\tau^{+}\tau^{-}$ & 0 & 670 & $2.4\times 10^{-21}$ \\
& 0.2 & 650 & $9.1\times 10^{-22}$ \\
& 0.4 & 660 & $1.8\times 10^{-21}$ \\
\enddata
\tablecomments{Limits are for different integration regions and DM particle mass $m_{\chi}$ derived from the VERITAS gamma-ray flux upper limits presented in this work.}
\end{deluxetable}

>>>>

\documentclass[12pt,manuscript]{aastex}
%\documentclass[twocolumn]{emulateapj}

@@

\begin{deluxetable}{cccccccccccc}
\tablecolumns{12}
\tablewidth{0pc}
\tablecaption{Constraints on relative CR pressure in the Coma cluster core for different spatial extensions} \rotate
\tabletypesize{\small}
\tablehead{
\colhead{RoI\tablenotemark{a} [deg]} 
    & \colhead{$F_\rmn{sim}(E)$\tablenotemark{b}} & \colhead{$F_\rmn{sim}(>E)$\tablenotemark{c}} 
    & \multicolumn{3}{c}{analytic model: $X_{\CR,\,\rmn{max}}~[\%]$\tablenotemark{d} } 
    & \multicolumn{3}{c}{$F_{\gamma,\,\rmn{min}}(>E)$\tablenotemark{e}} 
    & \multicolumn{3}{c}{$X_{\CR,\,\rmn{min}}~[\%]$\tablenotemark{f} } \\
& & & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
    & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
    & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
}
\startdata
\multicolumn{12}{l}{VERITAS constraints:}\\
0    & -     & -    & 10   & 23 & 97 & 1.6 & 0.7 & 0.3 & 0.067 & 0.061 & 0.11 \\
0.2  & 0.80  & 2.9  & 4.8  & 10 & 43 & 3.1 & 1.4 & 0.6 & 0.078 & 0.072 & 0.13 \\
0.4  & 1.21  & 4.4  & 6.7  & 15 & 62 & 6.3 & 2.8 & 1.3 & 0.098 & 0.090 & 0.16 \\
\hline
\multicolumn{12}{l}{{\em Fermi} constraints:}\\
0    & -  & -  & 3.2 & - & 3.0 & ~~3.5 & - & ~~6.4 & 0.067 & 0.061 & 0.11 \\
0.2  & -  & -  & 2.3 & - & 2.1 & ~~6.8 & - &  12.5 & 0.078 & 0.072 & 0.13 \\
0.4  & -  & -  & 1.7 & - & 1.5 &  13.5 & - &  25.0 & 0.098 & 0.090 & 0.16 \\
\enddata
\tablenotetext{a}{Intrinsic source radius (zero means point source), which is convolved with the analysis PSF.}
\tablenotetext{b}{Differential gamma-ray flux $E^{2}dF/dE$ at $E=220$ GeV in units of $10^{-6}$ GeV m$^{-2}$ s$^{-1}$ in the simulation-based analytic model by \citet{article:PinzkePfrommer:2010}. }
\tablenotetext{c}{Integrated gamma-ray flux above $E=220~\rmn{GeV}$ in units of $10^{-9}$ ph. m$^{-2}$ s$^{-1}$; simulation-based analytical model by \citet{article:PinzkePfrommer:2010}.} 
\tablenotetext{d}{Constraint on the relative CR pressure, $X_{\CR} = \expval{P_\CR}/ \expval{P_\rmn{th}}$, which was assumed to be constant through the cluster and calculated according to \citet{article:PfrommerEnsslin:2004b}.}
\tablenotetext{e}{Minimum gamma-ray flux of the hadronic model described in the
  text. Values are in units of $10^{-10}$ ph. m$^{-2}$ s$^{-1}$ (VERITAS) and
  $10^{-8}$ ph. m$^{-2}$ s$^{-1}$ {\em (Fermi)}.}
\tablenotetext{f}{Minimum relative CR pressure, $X_{\CR,\,\rmn{min}} = F_{\rmn{min}}/F$ in the hadronic model described in the text.}
\label{table:constraints}
\end{deluxetable}

\begin{deluxetable}{ccccccc}
\tablecolumns{4}
\tablewidth{0pc}
\tablecaption{Constraints on magnetic fields in the hadronic model of the Coma radio halo}
\tablehead{
 &
\multicolumn{6}{c}{Minimum magnetic field, $B_0~[\mu\rmn{G}]$}\\
 & \multicolumn{3}{c}{VERITAS constraints:} & \multicolumn{3}{c}{{\em Fermi} constraints:} \\
\colhead{$\alpha_{B}$}
 & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
 & \colhead{$\alpha=2.1$} & \colhead{$\alpha=2.3$} & \colhead{$\alpha=2.5$}
}
\startdata
0.3 & 0.61 & 0.51 & 0.43 & 1.26 & - & ~~2.69 \\
0.5 & 0.82 & 0.68 & 0.58 & 1.75 & - & ~~4.44 \\
0.7 & 1.19 & 0.98 & 0.83 & 2.75 & - &  14.6~ 
\enddata
\tablecomments{The parameters of the magnetic field are the magnetic decline, $\alpha_B$, and the central field strength, $B_{0}$, which are defined by $B(r) = B_{0}\,[n_\rmn{e}(r)/n_{\rmn{e}}(0)]^{\alpha_B}$.}
\label{table:Bmin}
\end{deluxetable}

@@

\begin{deluxetable}{lccc}
\tablecolumns{4}
\tablewidth{0pc}
\tablecaption{Limits on the DM annihilation cross section $\expval{\sigma v}$}
\tablehead{
\colhead{Channel} & RoI [deg] & $m_{\chi}$ [GeV] & $\expval{\sigma v}$ [cm$^{3}$ s$^{-1}$]
}
\startdata
W$^{+}$W$^{-}$ & 0 & 2000 & $1.1\times 10^{-20}$ \\
& 0.2 & 1900 & $4.3\times 10^{-21}$ \\
& 0.4 & 1900 & $8.4\times 10^{-21}$ \\
$b\bar{b}$ & 0 & 3500 & $1.2\times 10^{-20}$ \\
& 0.2 & 3400 & $4.4\times 10^{-21}$ \\
& 0.4 & 3500 & $8.7\times 10^{-21}$ \\
$\tau^{+}\tau^{-}$ & 0 & 670 & $2.4\times 10^{-21}$ \\
& 0.2 & 650 & $9.1\times 10^{-22}$ \\
& 0.4 & 660 & $1.8\times 10^{-21}$ \\
\enddata
\tablecomments{Limits are for different integration regions and DM particle mass $m_{\chi}$ derived from the VERITAS gamma-ray flux upper limits presented in this work.}
\end{deluxetable}
